---
title: "Armed Services Committees NOMINATE Visualization"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Armed Services Committee Rosters
# The membership for the House and Senate Armed Services Committees (including the House National Security Committee in the XXX and XXX Congresses) was derived from the committees' reports of activities.
# Committees published these reports on varying schedules, sometimes long after the Congress to which they referred. The reports were unavailable for some Congresses, and I assembled membership information from other sources, including C-SPAN hearings, which often list the committee membership.
# These lists include ALL members of the committee during that Congress, including those who left the committee or joined late. There are a few exceptions, for instance in the 102nd Congress, I included Mary Bono but not Sonny Bono because he died at the beginning of the session and played no part in the hearings covered by this project.
# There are several issues with NOMINATE scores, but they are the most readily available and consistent measure of ideology.
# 1. NOMINATE scores are consistent for a single member across their membership in a legislative body, so they do not capture ideological evolution. Therefore, these measures may under- or overstate a member's ideological extremism at any given point. 
# 2. The NOMINATE dimensions do not directly address military and national security issues. It is possible that there are outliers who score extremely conservative on the economic or racial scale by are liberal on national security issues. However, that seems less likely during the period of this study--for instance Democrats like Joe Lieberman who were hawkish and conservative on national security were also among the most conservative members of their party on other issues. 

## Code

# Load required libraries

```{r}
library(tidyverse)
library(dplyr)
# library(here) could not get this to work with Proton Drive
```
# Set home folder
```{r}
# here::i_am("/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/")
#> here() starts at /Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation
```
# Load data

```{r}
hasc102 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/HASC_102.csv")
hasc103 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_103.csv")
hasc104 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_104.csv")
hasc105 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_105.csv")
hasc106 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_106.csv")
hasc107 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_107.csv")
hasc108 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_108.csv")
hasc109 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_109.csv")
hasc110 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_110.csv")
hasc111 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_111.csv")
hasc112 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_112.csv")
hasc113 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_113.csv")
hasc114 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_114.csv")
sasc102 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_102.csv")
sasc103 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_103.csv")
sasc104 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_104.csv")
sasc105 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_105.csv")
sasc106 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_106.csv")
sasc107 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_107.csv")
sasc108 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_108.csv")
sasc109 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_109.csv")
sasc110 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_110.csv")
sasc111 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_111.csv")
sasc112 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_112.csv")
sasc113 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_113.csv")
sasc114 <- read_csv("~/Library/CloudStorage/ProtonDrive-james.vizzard@proton.me-folder/James/201801-20YYMM_PhD/P_Dissertation/data/NOMINATE/SASC_114.csv")

```

## Plots

```{r, echo=FALSE}
knitr::opts_chunk$set(fig.width = 3.25, fig.height = 2)

# plot of HASC in 102nd Congress
ph102 <- ggplot(data = hasc102,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 102nd Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Pointplot_HASC_102.png")

bh102 <- ggplot(data = hasc102,
            mapping = aes(x = Party, y = NOMINATE_DIM1))
bh102 + geom_boxplot() +
labs (X = "Party", Y = "DW-NOMINATE DIM1",
      title = "Ideological Distribution",
      subtitle = "HASC, 102nd Congress",
      caption = "Source: DW-NOMINATE")
ggsave(filename = "Boxplot_HASC_102.png")

#This is where I stopped on the night of 5 January. Need to figure out how to label the means and probably the extremes and then copy to the other congresses/Senate

# plot of HASC in 103d Congress
ph103 <- ggplot(data = hasc103,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 103d Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_103.png")

# plot of HASC in 104th Congress
ph104 <- ggplot(data = hasc104,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph104 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 104th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_104.png")

# plot of HASC in 105th Congress
ph105 <- ggplot(data = hasc105,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph105 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 105th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_105.png")

# plot of HASC in 106th Congress
ph106 <- ggplot(data = hasc106,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph106 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 106th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_106.png")

# plot of HASC in 107th Congress
ph107 <- ggplot(data = hasc107,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph107 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 107th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_107.png")

# plot of HASC in 108th Congress
ph108 <- ggplot(data = hasc108,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph108 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 108th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_108.png")

# plot of HASC in 109th Congress
ph109 <- ggplot(data = hasc109,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph104 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 109th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_109.png")

# plot of HASC in 110th Congress
ph110 <- ggplot(data = hasc110,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph110 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 110th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_110.png")

# plot of HASC in 111th Congress
ph111 <- ggplot(data = hasc111,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph111 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 111th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_111.png")

# plot of HASC in 112th Congress
ph112 <- ggplot(data = hasc112,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph104 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 112th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_112.png")

# plot of HASC in 113th Congress
ph113 <- ggplot(data = hasc113,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph104 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 113th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_113.png")

# plot of HASC in 114th Congress
ph114 <- ggplot(data = hasc114,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ph114 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "HASC, 114th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_HASC_114.png")

# plot of SASC in 102nd Congress
ps102 <- ggplot(data = sasc102,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 102nd Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_102.png")

# plot of SASC in 103d Congress
ps103 <- ggplot(data = sasc103,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 103d Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_103.png")

# plot of SASC in 104th Congress
ps104 <- ggplot(data = sasc104,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 104th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_104.png")

# plot of SASC in 105th Congress
ps105 <- ggplot(data = sasc105,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 105th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_105.png")

# plot of SASC in 106th Congress
ps106 <- ggplot(data = sasc106,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 106th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_106.png")

# plot of SASC in 107th Congress
ps107 <- ggplot(data = sasc107,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 107th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_107.png")

# plot of SASC in 108th Congress
ps108 <- ggplot(data = sasc108,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 108th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_108.png")

# plot of SASC in 109th Congress
ps109 <- ggplot(data = sasc109,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 109th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_109.png")

# plot of SASC in 110th Congress
ps110 <- ggplot(data = sasc110,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 110th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_110.png")

# plot of SASC in 111th Congress
ps111 <- ggplot(data = sasc111,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 111th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_111.png")

# plot of SASC in 112th Congress
ps112 <- ggplot(data = sasc112,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 112th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_112.png")

# plot of SASC in 113th Congress
ps113 <- ggplot(data = sasc113,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 113th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_113.png")

# plot of SASC in 114th Congress
ps114 <- ggplot(data = sasc114,
            mapping = aes(x = NOMINATE_DIM1, y = NOMINATE_DIM2, color = Party))
ps102 + geom_point() +
  scale_color_manual(values=c("blue", "red")) +
labs(x = "Liberal / Conservative (econ)", y = "Intraparty",
     title = "Ideological Distribution",
     subtitle = "SASC, 114th Congress",
     caption = "Source: DW-NOMINATE")
ggsave(filename = "Plot_SASC_114.png")
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
